\chapter*{Conclusion and perspectives}
\addcontentsline{toc}{chapter}{Conclusion and perspectives}
\markboth{Conclusion and perspectives}{}
In the development of critical systems, ensuring that the system adheres to its specified requirements is paramount. Verification, as a crucial phase in this process, provides a mechanism to validate that the system’s implementation aligns with its intended design. Throughout this report, we have explored and extended various approaches to enhance the effectiveness of verification, particularly through model-based testing.

We began by contextualizing the problem within the scope of validation and verification of critical systems, where both formal verification and testing play vital roles. In this context, we examined two primary approaches: SOG-based testing and Optimal LTS-based testing. The former reduces the complexity of Petri net models, while the latter optimizes the generation of test paths.

Our contribution lies in the integration of two key approaches, which includes a comprehensive process of Analysis and Verification, Correction and Improvement, and Evaluation and Testing. In extending this integration, we focused on incorporating machine learning techniques, with a particular emphasis on the critical dataset generation phase. This focus is fundamental to the success of the integrated approach, as it significantly enhances the framework's ability to manage large-scale systems and improve test generation. Additionally, we thoroughly tested the approach through numerous examples to validate its effectiveness and robustness.

As part of this work, the results of our integrated approach were documented in a scientific paper entitled \textit{Optimizing Label Coverage using Regular Expression-based Linear Programming}. This paper was submitted to and accepted by the VECoS 2024 International Conference on Verification and Evaluation of Computer and Communication Systems. The acceptance of this paper further validates the importance and impact of our contributions within the verification community.

Looking forward, the perspectives of this work include the implementation of AI-driven tools for transition coverage in Petri nets, the extension of coverage criteria to encompass other aspects such as place coverage, data flow, and specification coverage, and the adaptation of our methodology to model checking using Linear Temporal Logic (LTL). These advancements will further solidify the role of verification in the development of reliable and robust critical systems.