\chapter*{\huge Acknowledgements}
\begin{center}
\noindent
I am sincerely grateful to all those who supported and contributed to the realization of this final-year project.

First and foremost, I would like to express my deepest and most heartfelt thanks to my professional supervisor, \textbf{Mr. Souheib Baarir}, whose exceptional guidance, patience, and human warmth accompanied me throughout this journey. More than a supervisor, he was like a father to me always present, always understanding, always encouraging. His trust and unwavering support gave me the strength and confidence to move forward. I will forever be grateful for his generosity, kindness, and availability.

I would also like to thank my academic supervisor, \textbf{Mrs. Sana Younes}, for her involvement and thoughtful follow-up during the internship. Her guidance and feedback were highly appreciated.

My sincere thanks go to \textbf{Mrs. Anissa Kheireddine}, whose support and encouragement helped me during this incredible opportunity. I am truly grateful for her help and kindness.

I would like to warmly thank \textbf{Mr. Mohamed Taha Bennani} and \textbf{Mr. Kais Klai} for their trust and for believing in me from the start.

I also express my deep appreciation to the jury members: the president of the jury, \textbf{Mrs. Zouhour Ben Dhiaf}, and the reviewer of my report, \textbf{Mrs. Saloua Zammeli}, for accepting to evaluate my work. I hope this report meets their expectations in both content and clarity.

Finally, I would like to extend my gratitude to the entire teaching team of the Faculty of Sciences of Tunis for the solid academic foundation they provided, and to all those  near or far  who contributed in any way to the success of this project.

\end{center}
